---
title: "make-data for tartare?"
author:
- name: Christian Panse
  affiliation: Functional Genomics Center Zurich
  email: cp@fgcz.ethz.ch
- name: Tobias Kockmann
  affiliation: Functional Genomics Center Zurich
  email: tobias.Kockmann@fgcz.ethz.ch
package: tartare
output:
  BiocStyle::html_document
abstract: |
  xxx xxx xxx `r Githubpkg("rformassspectrometry/Spectra")`  [@Huber2015, @Trachsel2018]
vignette: |
  %\VignetteIndexEntry{Howto use the package?}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
bibliography:
  - tartare.bib
---

# Sample description

Pierce HeLa protein digest standard (#1862824, Thermo Scientific) in 3% ACN, 0.1% FA

# Data recording

## Q Exactive HF-X



### LC

200 ng sample were seperated on a linear gradient from 5 to 35% B in 20 min using a binary mobile phase composed of A) 0.1% FA in water, B) 0.1% FA in ACN. The stationary phase was ...

### MS

The MS acquision was started 18 min post sample injection and lastet only 4 min. Be aware that spray voltage and source gas was turned on at 18.5 min (see Tunefiles section of the method). This means the first 30 s were recorded without ESI. In summary, 4 different experiments were recorded

- Full MS / dd-MS² (TopN)
- PRM
- Targeted-SIM
- DIA

Experiment 2 and 3 were executed in parrallel! All method details are listed below.

Method of Q Exactive HF-X

Overall method settings

Global Settings
Use lock masses                                                         best 
Lock mass injection                                                        ― 
Chrom. peak width (FWHM)                                                  15 s
Time
Method duration                                                         4.00 min
Customized Tolerances (+/-)
Lock Masses                                                                ― 
Inclusion                                                                  ― 
Exclusion                                                                  ― 
Neutral Loss                                                               ― 
Mass Tags                                                                  ― 
Dynamic Exclusion                                                          ― 

                                  Experiments

Full MS / dd-MS² (TopN)
General
Runtime                                                               0 to 1 min
Polarity                                                            positive 
In-source CID                                                            0.0 eV
Default charge state                                                       2 
Inclusion                                                                  ― 
Exclusion                                                                  ― 
Tags                                                                       ― 
Full MS
Microscans                                                                 1 
Resolution                                                           120,000 
AGC target                                                               3e6 
Maximum IT                                                               100 ms
Number of scan ranges                                                      1 
Scan range                                                       200 to 2000 m/z
Spectrum data type                                                  Centroid 
dd-MS² / dd-SIM
Microscans                                                                 1 
Resolution                                                            30,000 
AGC target                                                               1e5 
Maximum IT                                                                50 ms
Loop count                                                                 5 
MSX count                                                                  1 
TopN                                                                       5 
Isolation window                                                         1.4 m/z
Isolation offset                                                         0.0 m/z
Scan range                                                       200 to 2000 m/z
Fixed first mass                                                           ― 
(N)CE / stepped (N)CE                                                nce: 30 
Spectrum data type                                                  Centroid 
dd Settings
Minimum AGC target                                                    8.00e3 
Intensity threshold                                                    1.6e5 
Apex trigger                                                               ― 
Charge exclusion                                    unassigned, 1, 5 - 8, >8 
Multiple charge states                                                   all 
Peptide match                                                      preferred 
Exclude isotopes                                                          on 
Dynamic exclusion                                                       10.0 s
If idle ..                                                do not pick others 

PRM
General
Runtime                                                               1 to 2 min
Polarity                                                            positive 
In-source CID                                                            0.0 eV
Dynamic RT                                                               off 
Default charge state                                                       2 
Inclusion                                                                 on 
MS²
Microscans                                                                 1 
Resolution                                                            30,000 
AGC target                                                               2e5 
Maximum IT                                                               100 ms
Loop count                                                                11 
MSX count                                                                  1 
MSX isochronous ITs                                                       on 
Isolation window                                                         4.0 m/z
Isolation offset                                                         0.0 m/z
Fixed first mass                                                           ― 
(N)CE / stepped (N)CE                                                nce: 35 
Spectrum data type                                                  Centroid 

Full MS — SIM
General
Runtime                                                               1 to 2 min
Polarity                                                            positive 
In-source CID                                                            0.0 eV
Full MS — SIM
Microscans                                                                 1 
Resolution                                                           120,000 
AGC target                                                               3e6 
Maximum IT                                                               200 ms
Number of scan ranges                                                      2 
Scan range 1                                                     150 to 1000 m/z
Scan range 2                                                    1000 to 2000 m/z
Spectrum data type                                                  Centroid 

Targeted-SIM
General
Runtime                                                               2 to 3 min
Polarity                                                            positive 
In-source CID                                                            0.0 eV
Inclusion                                                                 on 
SIM
Microscans                                                                 1 
Resolution                                                           240,000 
AGC target                                                               5e4 
Maximum IT                                                               200 ms
MSX count                                                                  5 
Isolation window                                                         4.0 m/z
Isolation offset                                                         0.0 m/z
Scan range                                                       150 to 2000 m/z
Spectrum data type                                                  Centroid 

DIA
General
Runtime                                                               3 to 4 min
Polarity                                                            positive 
In-source CID                                                            0.0 eV
Default charge state                                                       2 
DIA
Microscans                                                                 1 
Resolution                                                            30,000 
AGC target                                                               1e6 
Maximum IT                                                              auto 
Loop count                                                                11 
MSX count                                                                  1 
MSX isochronous ITs                                                       on 
Isolation window                                                        20.0 m/z
Isolation offset                                                         0.0 m/z
Fixed first mass                                                       100.0 m/z
(N)CE / stepped (N)CE                                                nce: 30 
Spectrum data type                                                  Centroid 

                                     Setup

Tunefiles
General
Switch Count  2
Base Tunefile C:\Xcalibur\methods\nogas_novoltage_nano.mstune
Element 1
At            0.50 min
New Tunefile  C:\Xcalibur\methods\default_nano.mstune
Element 2
At            34.50 min
New Tunefile  C:\Xcalibur\methods\nogas_novoltage_nano.mstune

Contact Closure
General
Used              True 
Start in Closed  False 
Switch Count         2 
Element 1
At                0.50 min
Switches to       Open 
Element 2
At               34.50 min
Switches to     Closed 

Syringe
General
Used                  False 
Start in OFF           True 
Stop at end of run    False 
Switch Count              0 
Pump setup
Syringe type       Hamilton 
Flow rate             3.000 µL/min
Inner diameter        2.303 mm
Volume                  250 µL

Divert Valve A
General
Used         False 
Start in 1-2  True 
Switch Count     0 

Divert Valve B
General
Used         False 
Start in 1-2  True 
Switch Count     0 

Lock Masses
    2 entries
     Mass Polarity Start   End Comment
    [m/z]          [min] [min] 
371.10124 Positive             
445.12002 Positive             

Inclusion List
    16 entries
     Mass Formula Species  CS Polarity Start   End (N)CE MSX ID Comment
    [m/z]     [M]         [z]          [min] [min]              
487.25671                   2 Positive  1.00  3.00    28        LGGNEQVTR
                                                                (light)
644.82261                   2 Positive  1.00  3.00    28        GAGSSEPVTGLDAK
                                                                (light)
683.82789                   2 Positive  1.00  3.00    28        VEATFGVDESNAK
                                                                (light)
547.29804                   2 Positive  1.00  3.00    28        YILAGVENSK
                                                                (light)
669.83806                   2 Positive  1.00  3.00    28        TPVISGGPYEYR
                                                                (light)
683.85371                   2 Positive  1.00  3.00    28        TPVITGAPYEYR
                                                                (light)
699.33842                   2 Positive  1.00  3.00    28        DGLDAASYYAPVR
                                                                (light)
726.83571                   2 Positive  1.00  3.00    28        ADVTPADFSEWSK
                                                                (light)
622.85351                   2 Positive  1.00  3.00    28        GTFIIDPGGVIR
                                                                (light)
636.86916                   2 Positive  1.00  3.00    28        GTFIIDPAAVIR
                                                                (light)
776.92975                   2 Positive  1.00  3.00    28        LFLQFGAQGSPFLK
                                                                (light)
410.00000                   2 Positive  3.00  4.00    28        window1
430.00000                   2 Positive  3.00  4.00    28        window2
450.00000                   2 Positive  3.00  4.00    28        window3
470.00000                   2 Positive  3.00  4.00    28        window4
490.00000                   2 Positive  3.00  4.00    28        window5

Exclusion List
   (no entries)

Neutral Losses
   (no entries)

Mass Tags
   (no entries)

## Fushion Lumos

# raw2mzML conversion



# Make Data (replaces `make-data.R`)




# Uploading to S3
```
#!/bin/bash

aws --profile AnnotationContributor s3 cp NestLink/F255744.RData s3://annotation-contributor/NestLink/F255744.RData --acl public-read

aws --profile AnnotationContributor s3 cp NestLink/WU160118.RData s3://annotation-contributor/NestLink/WU160118.RData --acl public-read

aws --profile AnnotationContributor s3 cp NestLink s3://annotation-contributor/NestLink --recursive --acl public-read

```
# Overview/Getting started using Bioconductor `r Biocpkg("ExperimentHub")`

load metadata

```{r eval=TRUE}
#library(kable)
fl <- system.file("extdata", "metadata.csv", package='tartare')
(metadata <- read.csv(fl, stringsAsFactors=FALSE))
```

query and load `r Biocpkg("NestLink")` package data from aws s3

```{r echo=TRUE, message=FALSE, warning=FALSE, eval=FALSE}
library(ExperimentHub)

eh <- ExperimentHub(); 
query(eh, "tartare")

# load(query(eh, c("NestLink", "F255744.RData"))[[1]])
# dim(F255744)
# load(query(eh, c("NestLink", "WU160118.RData"))[[1]])
# dim(WU160118)
```


# Session info

Here is the compiled output of `sessionInfo()`:

```{r sessionInfo, echo=FALSE}
sessionInfo()
```

# References
